Seagrass mapping and monitoring along the coasts of Crete, Greece

### 2011-01-31 MScDiplom_Lemenkova.tex
written Recommendations

\section*{Document Outline}
	\markright{Structure of the MSc Thesis}
	\addcontentsline{toc}{section}{Document Outline}
\textit{Chapter 1}: \nameref{sec:1} is an introductory section. It describes general background of the research problem, outlines the need and actuality of the problem (including the environmental vulnerability of the seagrasses), and highlights limitations and possibilities of the remote sensing application for the current work. In this chapter we also set up research objectives, put research questions for hypothesis testing and sketch research approach for the proposed work.\\
In \textit{Chapter 2}: \nameref{sec:2} we review the existing literature and reported research experience on the similar problem: studies of spectral separability of various seafloor types, limitations and advantages of the remote sensing techniques applied for seagrass mapping seagrass ecology and mapping seagrass environment. We considered not only the Mediterranean environment, but also papers from Australian and Chinese scientists, because seagrass monitoring is most actively developed in the southern regions of our planet. The review of the existing RTM algorithms for the retrieval of the optical parameters, as well as description of various tools for the spectrometric measurements - are given in the same Chapter as well. More close attention has been given to the imaging hyperspectral radiometer Trios RAMSES, used for the data collection.\\
\textit{Chapter 3}: \nameref{sec:3} deals with the methods and materials used in current work. We start our discussion from the fieldwork area location and describe tools and instruments used during the fieldwork, as well as sampling design. Procedures of the data pre-processing and capturing imagery from the Google Earth are also presented in the same chapter. \\
\textit{Chapter 4}: \nameref{sec:4} presents to the reader the main results of the current MSc work, obtained during the processing fieldwork and other collected data. It starts from the review of the collected data from different sources, then describes the modelling component of the research, namely WASI colour simulation and plotted resulting graphs. We also discuss here the particularities of various sensors, suitable enough for deriving radiometric information to discriminate sand from the seagrass. Furthermore, this chapter includes analysis of the spectral signatures of various seafloor cover types in conditions of changing environment, possibility and limitations for \textit{P.oceanica} spectral discrimination, statistical analysis of the data sets and mapping based on images processing.\\
\textit{Chapter 5}: \nameref{sec:5} summarizes and briefly discusses again the main results, reported in detail in a previous chapter. This chapter proposes some final discussions to the reader, and comes to the main research outcomes.\\
Finally, we suggest some recommendations for any further research focusing on the seagrass environment along the coasts of Crete (or other Mediterranean areas) in the final \textit{Chapter 6}: \nameref{sec:6}.\\
A lot of plotted graphs, statistical outcomes, tables, auxiliary (yet relevant to our research) pictures and images, illustrating our work - are collected in the \nameref{app}. Due to the standard editorial limitations of the current MSc work, it was not possible to include all them to the main chapters. However, we tried to make the structure of the Appendices most clear and easy-readable as possible, by dividing the Appendices into 10 various sub-sections and referencing to them from the main text where necessary. \\
The \nameref{bib} section includes literature and internet resources used for the current work. The cross-referencing and web hyper-referencing are used in the whole document to make reading more quick, effective and informative.

@@

\section{Recommendations}\label{sec:6}

\section{Keywords}
\markright{Keywords}
Seagrass, \textit{P.oceanica}, analysis of spectral reflectance, remote sensing, monitoring, Google Earth, Crete
\pagebreak

>>>>

\section*{Document Outline}
	\markright{Structure of the MSc Thesis}
	\addcontentsline{toc}{section}{Document Outline}
\textit{Chapter 1}: \nameref{sec:1} is an introductory section. It describes general background of the research problem, outlines the need and actuality of the problem (including the environmental vulnerability of the seagrasses), and highlights limitations and possibilities of the remote sensing application for the current work. In this chapter we also set up research objectives, put research questions for hypothesis testing and sketch research approach for the proposed work.\\
In \textit{Chapter 2}: \nameref{sec:2} we review the existing literature and reported research experience on the similar problem: studies of spectral separability of various seafloor types, limitations and advantages of the remote sensing techniques applied for seagrass mapping seagrass ecology and mapping seagrass environment. We considered not only the Mediterranean environment, but also papers from Australian and Chinese scientists, because seagrass monitoring is most actively developed in the southern regions of our planet. The review of the existing RTM algorithms for the retrieval of the optical parameters, as well as description of various tools for the spectrometric measurements - are given in the same Chapter as well. More close attention has been given to the imaging hyperspectral radiometer Trios RAMSES, used for the data collection.\\
\textit{Chapter 3}: \nameref{sec:3} deals with the methods and materials used in current work. We start our discussion from the fieldwork area location and describe tools and instruments used during the fieldwork, as well as sampling design. Procedures of the data pre-processing and capturing imagery from the Google Earth are also presented in the same chapter. \\
\textit{Chapter 4}: \nameref{sec:4} presents to the reader the main results of the current MSc work, obtained during the processing fieldwork and other collected data. It starts from the review of the collected data from different sources, then describes the modelling component of the research, namely WASI colour simulation and plotted resulting graphs. We also discuss here the particularities of various sensors, suitable enough for deriving radiometric information to discriminate sand from the seagrass. Furthermore, this chapter includes analysis of the spectral signatures of various seafloor cover types in conditions of changing environment, possibility and limitations for \textit{P.oceanica} spectral discrimination, statistical analysis of the data sets and mapping based on images processing.\\
\textit{Chapter 5}: \nameref{sec:5} summarizes and briefly discusses again the main results, reported in detail in a previous chapter. This chapter proposes some final discussions to the reader, and comes to the main research outcomes.\\
Finally, we suggest some recommendations for any further research focusing on the seagrass environment along the coasts of Crete (or other Mediterranean areas) in the final \nameref{sec:6}.\\
A lot of plotted graphs, statistical outcomes, tables, auxiliary (yet relevant to our research) pictures and images, illustrating our work - are collected in the \nameref{app}. Due to the standard editorial limitations of the current MSc work, it was not possible to include all them to the main chapters. However, we tried to make the structure of the Appendices most clear and easy-readable as possible, by dividing the Appendices into 10 various sub-sections and referencing to them from the main text where necessary. \\
The \nameref{bib} section includes literature and internet resources used for the current work. The cross-referencing and web hyper-referencing are used in the whole document to make reading more quick, effective and informative.

@@

\section*{Recommendations}\label{sec:6}
\markright{Recommendations}
\addcontentsline{toc}{section}{Recommendations}

To make further studies of \textit{P.oceanica} more effective we would suggest the following recommendations to be considered by the future researchers:
	\begin{description}
		\item[First:] To extend the research area towards the eastern part of the Crete Island, in order to received more regular observations of the 	seagrass locations.
		\item[Second:] To use different sources of imagery and thus, to increase the total collection of scenes covering the research area.
		\item[Third:] To extend the temporal period of the imagery coverage, once the data are available. The current work only includes images covering short temporal period (ca 10-year); further estimation of the dynamics of \textit{P.oceanica} along the coasts of Crete would increase our understanding of the long-scale temporal variations of the seagrass distribution.
		\item[Fourth:] To apply various classifications methods for the available imagery in order to compare the results received by means of various techniques
		\item[Fifth:] To simulate various environmental conditions while modelling optical properties of different seafloor cover types. Not only the depths and 	the chemical content of the seawater should be considered, but also other factors determining the effect of the ecology and health of \textit{P.oceanica}.
		\item[Sixth:] To consider seafloor geomorphology among other factors determining seagrass distribution. If possible, to find out bathymetric data for the research area, and to overlay them with existing images and maps, in order to analyse correlation between spatial distribution of seagrass \textit{P.oceanica} and underwater relief along Cretan coasts. 
		\item[Seventh:] Other RTM software may be tested and the modelling outcomes compared.
		\item[Eighth:] Application of various open source GIS (ILWIS, GRASS) could be very useful for the validation of the cartographic results, assessment of accuracy and comparison of various classification methods. 
		\item[Ninth:] The analysis of the health indicators of the seagrass (such as number of leaves per shoot, biomass estimation within the single shot, etc) was not considered in the current work, as it would go beyond the scope of the MSc thesis. However, ecological investigations could be used for the assessment of the vulnerability of the seagrass meadows in various locations on Crete. 
		\item[Tenth:] A flexible combination of the multi-scale mapping and results of the fieldwork measurements with GPS-referenced underwater footage would enable more profound analysis of the coastal environment on Crete. 
	\end{description}

\section*{Keywords}
\markright{Keywords}
\addcontentsline{toc}{section}{Keywords}
\textit{P.oceanica}, seagrass monitoring, spectral reflectance, remote sensing, WASI, Google Earth, Crete
\pagebreak
